{\ttfamily oomph-\/lib} is \char`\"{}open source\char`\"{} software and may therefore be freely downloaded and distributed -- the full details are given below. To facilitate the installation of the library, the {\ttfamily oomph-\/lib} distribution includes (parts of) certain other open source libraries (Super\+LU, M\+E\+T\+IS and B\+L\+AS). Redistribution of these libraries with {\ttfamily oomph-\/lib} has been approved by their authors -- we suggest you get in touch with them if you wish to re-\/distribute their libraries yet again.





\subsection*{{\ttfamily oomph-\/lib\textquotesingle{}s} licencing terms}

This library is free software; you can redistribute it and/or modify it under the terms of the \href{http://www.gnu.org/licenses/lgpl.html}{\tt G\+NU Lesser General Public License } as published by the \href{http://www.fsf.org/}{\tt Free Software Foundation} ; either version 2.\+1 of the License, or (at your option) any later version. This library is distributed in the hope that it will be useful, but W\+I\+T\+H\+O\+UT A\+NY W\+A\+R\+R\+A\+N\+TY; without even the implied warranty of M\+E\+R\+C\+H\+A\+N\+T\+A\+B\+I\+L\+I\+TY or F\+I\+T\+N\+E\+SS F\+OR A P\+A\+R\+T\+I\+C\+U\+L\+AR P\+U\+R\+P\+O\+SE. See the \href{http://www.gnu.org/licenses/lgpl.html}{\tt G\+NU Lesser General Public License } for more details.

~\newline
 ~\newline


Your use or distribution of {\ttfamily oomph-\/lib} or any derivative code implies that you agree to this License.

~\newline
 ~\newline
 Copyright (c) 2006-\/2018 by \href{http://www.maths.man.ac.uk/~mheil}{\tt Matthias Heil} and \href{http://www.maths.man.ac.uk/~ahazel}{\tt Andrew L. Hazel}.





\subsection*{Licencing details for Super\+LU}

The {\ttfamily oomph-\/lib} distribution includes the double precision versions of the sparse direct linear solver Super\+LU (version 3.\+0 of the serial version and version 2.\+0 of the distributed memory parallel version). Full details of the \href{http://crd.lbl.gov/~xiaoye/SuperLU}{\tt Super\+LU} licence may be found at \begin{center} \href{http://crd.lbl.gov/~xiaoye/SuperLU}{\tt http\+://crd.\+lbl.\+gov/$\sim$xiaoye/\+Super\+LU} \end{center} 





\subsection*{Licencing details for M\+E\+T\+IS}

The {\ttfamily oomph-\/lib} distribution includes version 4.\+0 of George Karypis\textquotesingle{} \href{http://www-users.cs.umn.edu/~karypis/metis/}{\tt M\+E\+T\+IS} mesh partitioning library. Full details of the \href{http://www-users.cs.umn.edu/~karypis/metis/}{\tt M\+E\+T\+IS} licence may be found at \begin{center} \href{http://www-users.cs.umn.edu/~karypis/metis/}{\tt http\+://www-\/users.\+cs.\+umn.\+edu/$\sim$karypis/metis/ } \end{center} 





\subsection*{Licencing details for B\+L\+A\+S/\+L\+A\+P\+A\+CK}

The {\ttfamily oomph-\/lib} distribution includes the entire B\+L\+AS library and a few functions from L\+A\+P\+A\+CK. Full licencing details for the \href{http://www.netlib.org/blas/}{\tt B\+L\+AS library} may be found at \begin{center} \href{http://www.netlib.org/blas/}{\tt http\+://www.\+netlib.\+org/blas/ } \end{center}  Full licencing details for the \href{http://www.netlib.org/lapack/}{\tt L\+I\+B\+R\+A\+RY library} may be found at \begin{center} \href{http://www.netlib.org/lapack/}{\tt http\+://www.\+netlib.\+org/lapack/ } \end{center} 





\subsection*{Licencing details for G\+MP}

The {\ttfamily oomph-\/lib} distribution includes version 6.\+1.\+2 of the G\+NU Multiple Precision Arithmetic Library (G\+MP), \href{https://gmplib.org}{\tt https\+://gmplib.\+org} which is released under the \href{https://www.gnu.org/licenses/lgpl.html}{\tt G\+NU L\+G\+PL v3} and \href{https://www.gnu.org/licenses/gpl-2.0.html}{\tt G\+NU G\+PL v2} licences. Full details of the licence may be found at \begin{center} \href{https://gmplib.org}{\tt https\+://gmplib.\+org} \end{center} 





\subsection*{Licencing details for M\+P\+FR}

The {\ttfamily oomph-\/lib} distribution includes version 3.\+1.\+6 of the G\+NU M\+P\+FR Library \href{http://www.mpfr.org/}{\tt http\+://www.\+mpfr.\+org/} which is released under the \href{http://www.gnu.org/copyleft/lesser.html}{\tt G\+NU Lesser General Public License} (G\+NU Lesser G\+PL).

Full details of the licence may be found at \begin{center} \href{http://www.mpfr.org/}{\tt http\+://www.\+mpfr.\+org/} \end{center} 





\subsection*{Licencing details for Boost}

The {\ttfamily oomph-\/lib} distribution includes version 1.\+65.\+1 of the Boost Library \href{http://www.boost.org/}{\tt http\+://www.\+boost.\+org/} which is released under the \href{http://www.boost.org/LICENSE_1_0.txt}{\tt Boost Software Licence Version 1.\+0}.

Full details of the licence may be found at \begin{center} \href{http://www.boost.org/users/license.html}{\tt http\+://www.\+boost.\+org/users/license.\+html} \end{center} 





\subsection*{Licencing details for C\+G\+AL}

The {\ttfamily oomph-\/lib} distribution includes version 4.\+11 of C\+G\+AL The Computational Geometry Algorithms Library \href{https://www.cgal.org/}{\tt https\+://www.\+cgal.\+org/} which is released under the distributed under a dual license scheme, that is under the \href{https://www.gnu.org/copyleft/gpl.html}{\tt G\+PL}/ \href{https://www.gnu.org/copyleft/lesser.html}{\tt L\+G\+PL} open source license, as well as under commercial licenses.

Full details of the licence may be found at \begin{center} \href{https://doc.cgal.org/latest/Manual/preliminaries.html#licenseIssues}{\tt https\+://doc.\+cgal.\+org/latest/\+Manual/preliminaries.\+html\#license\+Issues} \end{center} 







 

 \hypertarget{index_pdf}{}\section{P\+D\+F file}\label{index_pdf}
A \href{../latex/refman.pdf}{\tt pdf version} of this document is available. \end{document}
